### 2020-03-01 doc/icfp20/counterpoint.tex
typo

With this record type, we can show that the counterpoint in
Figure~\ref{fig:fs} is correct, since the music is an inhabitant of
the \texttt{FIrstSpecies} type.

>>>>

With this record type, we can show that the counterpoint in
Figure~\ref{fig:fs} is correct, since the music is an inhabitant of
the \texttt{FirstSpecies} type.
